---
title: "Tidy data"
author: "Your name"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE, cache = TRUE, messages = FALSE, warnings = FALSE
)
library(tidyverse)
```

# Lab Session 3

1. Download the [billboard data](http://earo.me/data/medascin17/billboard.csv). The `billboard` dataset contains the date a song first entered the Billboard Top 100 in 2000 and its rank over 76 weeks.
2. Read the dataset into R and take a look at the data.

```{r read}
# If you have downloaded the data to the local disk, just replace the url with
# the file path
billboard <- read_csv("http://earo.me/data/medascin17/billboard.csv")
billboard
```

3. Transform the data to the long data form named as `billboard_long`.
4. [Bonus] Split the `billboard_long` to two separate datasets as `song` and `rank`. The `song` data will include `artist`, `track`, `time` and a new column called `id` assigning a unique identifier for each song. The `rank` data will include the `id`, `date`, `week`, `rank` columns. The `id` column is the key variable that maintains the linking between two datasets.
